### 2020-01-09 nlp_models.tex
gpt2 figures added

\section{Comparison of NLP Transformer Models}
\label{sxn:cv}

>>>>

\section{Comparison of NLP Transformer Models}
\label{sxn:nlp}

\paragraph{GPT vs GPT2}

\paragraph{Power Law Exponents}

\begin{figure}
   \includegraphics[scale=0.25]{img/gpt-alpha-hist.png}
   \caption{Comparison of heavy tailed power law exponent $\alpha$ for OpenAI GPT and GPT pretrained models}

   \label{fig:gpt-alphs-hist}
\end{figure}

\begin{figure}[t]
    \centering

    \subfigure[ Power Law Exponent $\alpha$  ]{
        \includegraphics[width=4.5cm]{img/gpt2-alpha-hist.png}
        \label{fig:gpt-alpha-layer}
    }
    \qquad
    \subfigure[ Spectral Norm $\Vert\mathbf{W}\Vert_{\infty}$]{
        \includegraphics[width=4.5cm]{img/gpt2-snorm-hist.png}
        \label{fig:resnet-snorm-layer}
    }
    \qquad
    \subfigure[ Alpha-Norm $\Vert\mathbf{X}\Vert_{\alpha}^{\alpha}$]{
        \includegraphics[width=4.5cm]{img/gpt2-pnorm-hist.png}
        \label{fig:gpt-pnorm-layer}
    }
    \caption{Comparison of Power Law Exponnents, Spectral Norm, and Alpha-Norm for different size models in the GPT2 architecture series.    }
    \label{fig:gpt-alpha-layers}
\end{figure}

\paragraph{Correlation Flow}

\begin{figure}[t]
    \centering

    \subfigure[ Power Law Exponent $\alpha$  ]{
        \includegraphics[width=4.0cm]{img/gpt-alpha-layer.png}
        \label{fig:gpt-alpha-layer}
    }
    \qquad
    \subfigure[ Spectral Norm $\Vert\mathbf{W}\Vert_{\infty}$]{
        \includegraphics[width=4.5cm]{img/gpt-snorm-layer.png}
        \label{fig:resnet-snorm-layer}
    }
    \qquad
    \subfigure[ Alpha-Norm $\Vert\mathbf{X}\Vert_{\alpha}^{\alpha}$]{
        \includegraphics[width=4.5cm]{img/gpt-pnorm-layer.png}
        \label{fig:gpt-pnorm-layer}
    }
    \caption{Comparison of Correlation Flow and Spectral Norm for OpenAI GPT and GPT2   }
    \label{fig:gpt-alpha-layers}
\end{figure}

\paragraph{GPT2: small, medium, large, extra-large}
